---
title: "Data Cleaning"
format: html
editor: visual
---

```{r}
library(tidyverse)
```

# World Values Survey

These data are sourced from the [World Values Survey Wave 7 (2017-2022)](https://www.worldvaluessurvey.org/WVSDocumentationWV7.jsp), accessed March 26, 2023.

```{r}
WVS_raw <- read_csv("../WVS_Wave7.csv")
```

```{r}
head(WVS_raw)
```

First, we need to select only the nine countries analyzed by Jacobson (2017). These are those countries and their WVS Country Codes:

 - Kenya (404)
 - South Africa (710)
 - Brazil (76)
 - the United States (840)
 - India (356)
 - Thailand (764)
 - England and Wales (Great Britain, 826)
 - Hungary (348)
 - the Netherlands (528)
 - Australia (36)




# References

Haerpfer, Christian, Ronald Inglehart, Alejandro Moreno, Christian Welzel, Kseniya Kizilova, Jaime Diez-Medrano, Marta Lagos, Pippa Norris, Eduard Ponarin, and Bi Puranen. 2022. “World Values Survey Wave 7 (2017-2022) Cross-National Data-Set.” *World Values Survey*. Retrieved March 26, 2023 (https://www.worldvaluessurvey.org/WVSDocumentationWV7.jsp).